Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers

### 2023-05-29 2_SSL_NE/article/article_main.tex
completed latex layout modifications

% layout
\input{auxiliary/preamble/2_preamble_layout_report}

@@

M. Weinold$^{1,2,3}$, S. Kolesnikov$^3$, L.D. Anadon$^{3,4}$ \\
        "Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers" \textit{Environmental Science \& Technology} (2023) \\
        \newline
        $^1$ Technology Assessment Group, Paul Scherrer Institute, Switzerland \\
        $^2$ ETH Zurich, Zurich, Switzerland \\
        $^3$ CEENRG, Dept. of Land Economy, University of Cambridge, UK \\
        $^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Keywords}

@@

\section{Synopsis}

Understanding the underlying drivers of innovation in LEDs will enable better policy recommendations for a range of demand-side energy technologies, which will play a key role in climate change mitigation.

>>>>

% layout
\input{2_SSL_NE/article/auxiliary/preamble/2_preamble_layout_paperdraft}

@@

\begin{center}
    \large
    \textbf{Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers}
\end{center}

M. Weinold$^{1,2,3}$, S. Kolesnikov$^3$, L.D. Anadon$^{3,4}$ \\
\newline
$^1$ Technology Assessment Group, Paul Scherrer Institute, Switzerland \\
$^2$ ETH Zurich, Zurich, Switzerland \\
$^3$ CEENRG, Dept. of Land Economy, University of Cambridge, UK \\
$^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA

@@

\section*{Keywords}

@@
